A Parallel, Backjumping Subgraph Isomorphism Algorithm using Supplemental Graphs

### 2015-06-02 paper/paper.tex
JVM does parallel GC

Note that SND is not inherently multi-threaded, but the Java 8 virtual machine we used for testing
makes some use of multiple threads even for sequential code. On the one hand, this could be seen as
giving SND an unfair advantage. However, nearly all modern CPUs are multi-core anyway, so one could
say that it is everyone else's fault for not taking advantage of these extra resources. We therefore
present both sequential (from a dedicated implementation, \emph{not} a threaded implementation
running with only a single thread) and threaded results for our algorithm.

>>>>

Note that SND is not inherently multi-threaded, but the Java 8 virtual machine we used for testing
makes use of multiple threads for garbage collection even for sequential code. On the one hand,
this could be seen as giving SND an unfair advantage. However, nearly all modern CPUs are multi-core
anyway, so one could say that it is everyone else's fault for not taking advantage of these extra
resources. We therefore present both sequential (from a dedicated implementation, \emph{not} a
threaded implementation running with only a single thread) and threaded results for our algorithm.
